\City{San Antonio}

\newcommand*{\WWWhiteRd}{W\!.~W\!.~White~Rd}

\begin{LocationList}

\Location{Asuma \Rest \Weigh \Multiple}
On Applewhite~Rd in southwest San Antonio.
Take the exit for Zarzamora~St off \I{35}, then turn southeast.
Use the South Gate to access Asuma.
For the export facility and truck parking, follow the road and turn right at the end.
The factory loading docks are located near the southeast corner of the main building.

\Location{\GarageHQ \Garage}
On \TX[Loop]{13} \WWWhiteRd.

\Location{Global Mills}
Off Rittiman~Rd to the south, east of \I{35} in northeast San~Antonio.

\Location{Grand Pastures}
On \TX[FM]{539} southwest of \Town{Sutherland Springs}[,] off \US{87} southeast of San Antonio.

\Location{Kenworth \TruckDealer \Dealer \Rest \Service}
On the south side \I{10} access road by \Exit{581}, east of San Antonio.

\Location{Mary's Cotton}
On \US{57}, off \I{35} southwest of San Antonio.

\Location{NAMIQ}
Off \TX[FM]{306} to the southwest, west of \I{35}, north of San Antonio.

\Location{Olthon Homes}
On the west side \I{35} access road south of \TX[FM]{306}, north of San~Antonio.

\Location{Petrolucent}
Off \I{37} \Exit{76} to the northeast.

\Location{Plugged}
Next to the 42 Print warehouse, off \TX[Loop]{13} \WWWhiteRd\ north of \I{10} \Exit{580}.

\Location{\RecruitmentAgency \Recruitment}
On Gembler at Center~Pkwy off \TX[Loop]{13} \WWWhiteRd.

\Location{\TruckStop \Gas \Rest \Service \Weigh}
By \I{10} \Exit{581} east of San Antonio.

\Location{USBB}
On Houston at Center~Pkwy.
Take \TX[Loop]{13} \WWWhiteRd\ north from \I{10} \Exit{580} and turn left onto Gembler, then left again onto Center~Pkwy.

\Location{Vortex \UndergroundTank}
At the Henry's Ranch store on \TX[FM]{306} at the east side \I{35} access road, north of San Antonio.

\Location{Wallbert food warehouse}
Off Gembler to the north, west of \TX[Loop]{13} \WWWhiteRd.
Take~\I{10} \Exit{580} and head north.

\Location{Wallbert non-food market}
On Zarzamora~St at \TX[Loop]{13} Military~Dr, northwest of \I{35} \Exit{150}, in southwest San Antonio.

\end{LocationList}
