\City{Little Rock}

\begin{LocationList}

\Location{18 Wheels Garage \Garage \Gas \Service}
Outside \Town{Prothro Junction} off \I{40} to the north, east of Little Rock.
Truck services are across the street.

\Location{Epro Gas}
On Dixie~St off \US{70} Broadway~St to the north, east of \I{30}.

\Location{Faraday}
On \AR{333} outside \Town{London}[,] west of Little Rock.
Use \I{40} \Exit{78}.
% x: 65 miles from Little Rock

\Location{Flavorfair}
By Dixie~St off \US{70} Broadway~St to the north, east of \I{30}.

\Location{GARC Railroads}
Off \US{70} Broadway~St to the north at Dixie~St, east of \I{30}.

\Location{\GasStation \Gas \Rest}
In \Town{Prothro Junction} by \I{40}, east of Little Rock.
Truck parking is behind the motel across the street.

\Location{Global Sky}
Accessed from 9th~St, off \I{30} to the east.

\Location{International \TruckDealer \Dealer \Gas \Rest \Service \Weigh}
Next to the Driverse truck stop on \AR{331} in \Town{Russellville}[,] west of Little Rock.
Use \I{40} \Exit{84}.
% x: 40 miles from Little Rock

\Location{MWM}
Off \US{70} Broadway~St to the north at Dixie~St, east of \I{30}.

\Location{Pulaski County Airport}
The cargo terminal is only accessible via 9th~St, off \I{30} to the east.

\Location{\RecruitmentAgency \Recruitment}
Off \US{70} Broadway~St to the north, west of \I{30}.

\Location{Rock Port \SpecialTransport}
Off \US{70} Broadway~St to the south, east of \I{30}.
Follow signs for Taylor Construction Group.

\Location{Taylor}
Off \US{70} Broadway~St to the south, east of \I{30}.

\Location{X-Tech Machinery \SpecialTransport}
On Bethany~Rd in \Town{Prothro Junction}, off \I{40} to the south east of Little Rock.

\end{LocationList}
