\City{Redding}

\begin{LocationList}

\Location{Bushnell Farms farm}
On South~Ave west of \Town{Corning}[,] south of Redding.

\Location{Bushnell Farms livestock auction}
On \CA{273} Airport~Rd just south of Redding.

\Location{Coastline Mining}
On Spring Gulch~Rd off \CA{273} south of downtown Redding.

\Location{Deepgrove logging site}
Accessed from \CA{299} 10~miles west of \Town{Burney}[,] northeast of Redding.

\Location{Deepgrove sawmill}
On \CA{273} opposite Spring Gulch~Rd, south of downtown Redding.

\Location{Drake Car Dealer}
On Cypress~Ave, west of \I{5} in south Redding.

\Location{Freightliner \TruckDealer \Dealer \Rest \Service}
On Caterpillar~Rd, off \CA{273} Market~St to the west in northwest Redding.

\Location{\GarageHQ \Garage}
On Airport~Rd at Knighton~Rd in southeast Redding.

\Location{HMS Machinery}
On Spring Gulch~Rd off \CA{273} south of downtown Redding.

\Location{Home Store}
Off Cypress~Ave to the north, east of \I{5} in south Redding.

\Location{\RecruitmentAgency \Recruitment}
On Airport~Rd north of Knighton~Rd in southeast Redding.

\Location{Sell Goods}
On Airport~Rd north of Knighton~Rd in southeast Redding.

\Location{USBB}
On Caterpillar~Rd, off \CA{273} Market~St to the west in northwest Redding.

\Location{Wallbert food market}
By Dana~Dr off Victor~Ave, north of \CA{44} in east Redding.

\Location{Wallbert non-food warehouse}
On Airport~Rd north of Knighton~Rd in southeast Redding.

\Location{WP \UndergroundTank \Gas \Rest \Service \Weigh}
At the WP truck stop on Knighton~Rd, in south Redding by \I{5}.

\end{LocationList}
