
\City{Albuquerque}

\begin{LocationList}

\Location{42 Print}
East of 12th Street in southwest Albuquerque. Use \I{40} \Exit{157}.

\Location{ABQ Cargo Center}
At the airport cargo terminal in southeast Albuquerque. Use \I{25} \Exit{220}.

\Location{Bitumen}
South of Montaño Street in northwest Albuquerque. Use \I{25} \Exit{228}.

\Location{Charged}
Just northwest of \I{25} \Exit{228}, in northern Albuquerque.

\Location{\GarageHQ \Garage}
North of Montaño Street in northwest Albuquerque. Use \I{25} \Exit{228}.

\Location{Global Mills}
North of Montaño Street in northwest Albuquerque. Use \I{25} \Exit{228}.

\Location{HMS Machinery}
West of 12th Street in southwest Albuquerque. Use \I{40} \Exit{157}.

\Location{NAMIQ}
Just south of the airport, off \I{25} \Exit{220} to the southeast.

\Location{Peterbilt \TruckDealer \Dealer \Rest \Service}
West of 12th Street in southwest Albuquerque. Use \I{40} \Exit{157}.

\Location{Rail Export}
North of Rio Bravo Boulevard in southwest Albuquerque. Use \I{25} \Exit{220}.

\Location{Tidbit}
East of Louisiana Boulevard in northeast Albuquerque. Use \I{40} \Exit{162}.

\Location{\TruckStop \Gas \Rest}
Off Montgomery Boulevard in northeast Albuquerque. Use \I{25} \Exit{228} or frontage roads.

\Location{Ultimus}
On the tarmac at the airport cargo terminal in southeast Albuquerque. Use \I{25} \Exit{220}.

\Location{Voltison Motors car dealer}
South of Montaño Street in northwest Albuquerque. Use \I{25} \Exit{228}.

\Location{Voltison Motors warehouse}
By 12th Street in southwest Albuquerque. Use \I{40} \Exit{157}.

\Location{Wallbert}
North of Montaño Street in northwest Albuquerque. Use \I{25} \Exit{228}. The non-food warehouse is opposite the garage, the food warehouse to the northeast of it.

\end{LocationList}



% fix:
% ascii-fy "ñ" in Montaño St
% also consider output: the ñ is not parseable as such in the PDF unless T1 font encoding is used; see:
% https://tex.stackexchange.com/a/84382
